\documentclass[11pt,a4paper]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc} % Handles special characters
\usepackage[T1]{fontenc}    % Font encoding
\usepackage[left=1.5cm,right=1.5cm,top=2cm,bottom=2cm]{geometry} % Margins
\usepackage{helvet}         % Helvetica font (Swiss Style)
\usepackage{xcolor}         % Colors
\usepackage{hyperref}       % Links
\usepackage{enumitem}       % Custom lists

% --- SWISS STYLE SETTINGS ---
\renewcommand{\familydefault}{\sfdefault} % Force Sans-Serif font
\linespread{1.1}                          % Improve reading spacing
\setlength{\parindent}{0pt}               % No indentation
\pagestyle{empty}                         % Remove page numbers

% --- COLORS ---
\definecolor{swissred}{HTML}{FF3300}      % Accent Color (Swiss Red)
\definecolor{darkgray}{HTML}{333333}      % Text Color
\definecolor{lightgray}{HTML}{666666}     % Metadata Color

% --- LINK STYLES ---
\hypersetup{
    colorlinks=true,
    linkcolor=darkgray,
    urlcolor=swissred,
    pdfborder={0 0 0}
}

% --- CUSTOM COMMANDS ---

% 1. Section Layout (Left Label | Right Content)
\newcommand{\cvsection}[2]{
    \vspace{0.5cm}
    \noindent
    \begin{minipage}[t]{0.25\textwidth} % Left Column (Label)
        \vspace{0pt}
        \textcolor{swissred}{\textbf{\MakeUppercase{\footnotesize #1}}}
    \end{minipage}%
    \hfill
    \begin{minipage}[t]{0.72\textwidth} % Right Column (Content)
        \vspace{0pt}
        #2
    \end{minipage}
    \par
}

% 2. Job Entry Header
\newcommand{\jobtitle}[2]{
    \textbf{\large #1} \hfill {\footnotesize \color{lightgray} #2} \\
}

% --- DOCUMENT START ---
\begin{document}

% --- HEADER ---
\noindent
\begin{minipage}[b]{0.60\textwidth}
    \fontsize{32}{36}\selectfont \textbf{\MakeUppercase{John}} \\
    \textbf{\MakeUppercase{Doe}}
\end{minipage}%
\hfill
\begin{minipage}[b]{0.38\textwidth}
    \raggedleft % Right align text
    \small
    \href{mailto:hello@johndoe.com}{hello@johndoe.com} \\
    \href{https://linkedin.com/in/johndoe}{linkedin.com/in/johndoe} \\
    \href{https://github.com/johndoe}{github.com/johndoe} $\cdot$ \href{https://johndoe.com}{johndoe.com} \\
    {\color{lightgray} +1 555 019 2834}
\end{minipage}

\vspace{0.4cm}

% Red Accent Line
{\color{swissred}\hrule height 2pt}

% --- PROFILE ---
\cvsection{Profile}{
    Results-oriented Software Engineer with 5+ years of experience in full-stack development and cloud infrastructure.
    Proven track record of designing scalable systems and optimizing data pipelines.
    Passionate about open-source contribution and continuous integration standards.
}

% --- EXPERIENCE ---
\cvsection{Experience}{
    % JOB 1
    \jobtitle{Tech Solutions Inc.}{New York | Jan 2022 - Present}
    \textit{Senior Software Engineer} \\
    Leading a team of 5 developers in building a distributed fintech platform serving 1M+ users.
    \begin{itemize}[leftmargin=*, label={\color{swissred}\tiny$\blacksquare$}, itemsep=2pt, topsep=4pt]
        \item \textbf{System Architecture:} Redesigned the legacy monolith into microservices using Go and gRPC, reducing latency by 40\%.
        \item \textbf{CI/CD Pipeline:} Implemented an automated deployment pipeline using GitHub Actions and Docker, cutting deployment time from 1 hour to 10 minutes.
        \item \textbf{Mentorship:} Conducted code reviews and weekly technical workshops to upskill junior developers.
        \item \textbf{Optimization:} Optimized SQL queries and database indexing strategies, resulting in a 25\% reduction in AWS RDS costs.
    \end{itemize}
    \vspace{0.4cm}

    % JOB 2
    \jobtitle{Creative Startups Co.}{Remote | June 2019 - Dec 2021}
    \textit{Full Stack Developer}
    \begin{itemize}[leftmargin=*, label={\color{swissred}\tiny$\blacksquare$}, itemsep=2pt]
        \item \textbf{Frontend Development:} Built responsive single-page applications (SPA) using React and TypeScript.
        \item \textbf{API Integration:} Developed RESTful APIs with Node.js/Express and integrated third-party payment gateways (Stripe).
        \item \textbf{Testing:} Achieved 90\% code coverage by implementing unit and integration tests using Jest and Cypress.
    \end{itemize}
}

% --- PROJECTS ---
\cvsection{Projects}{
    % Project 1
    \jobtitle{OpenSource Analytics Tool}{2023}
    \textit{Python, Flask, PostgreSQL} \\
    A lightweight analytics tool for tracking website traffic without cookies. \\
    Featured on Hacker News and garnered 500+ stars on GitHub. \\
    \href{https://github.com/xxxxxxxxx/xxxxxxxxx}{View Source (GitHub)}
    \vspace{0.4cm}

    % Project 2
    \jobtitle{Smart Home Dashboard}{2022}
    \textit{IoT, Raspberry Pi, Vue.js} \\
    Created a centralized dashboard to monitor temperature, humidity, and energy usage in real-time using MQTT protocol. \\
    \href{https://github.com/xxxxxxxxx/xxxxxxxxxx}{View Source (GitHub)}
}

% --- SKILLS ---
\cvsection{Skills}{
    \textbf{Languages} \\
    Go, Python, TypeScript, JavaScript (ES6+), SQL, Bash
    \vspace{0.2cm}

    \textbf{Frameworks \& Libraries} \\
    React, Next.js, Django, Gin, Tailwind CSS
    \vspace{0.2cm}

    \textbf{Infrastructure \& Tools} \\
    Docker, Kubernetes, AWS (EC2, S3, Lambda), Terraform, Linux
    \vspace{0.2cm}

    \textbf{Spoken Languages} \\
    English (Native), German (B2), Spanish (A2)
}

% --- EDUCATION ---
\cvsection{Education}{
    \jobtitle{University of Technology}{2015 - 2019}
    \textit{B.Sc. Computer Science}
    \begin{itemize}[leftmargin=*, label={\color{swissred}\tiny$\blacksquare$}, itemsep=0pt, topsep=2pt]
        \item \textbf{Thesis:} Distributed Ledger Technology in Supply Chain Management.
        \item \textbf{Honors:} Dean's List 2018, 2019.
        \item \textbf{Societies:} President of the University Coding Club.
    \end{itemize}
}

\end{document}
